---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("AER")
data("Journals",package = "AER")
journals<-Journal[,c("subs","price")]
journals$citeprice<-journals$price/Journals$citations
#lm(journals$sub~journals$citeprice)
mm<-lm(subs~citeprice,data=journals)
```


```{r}
plot(log(subs)~log(citeprice), data=journals)
```


```{r}
mm<-lm(subs~citeprice,data=journals)
plot(mm)
```

```{r}
Journals<-read.csv("Journals.csv")
journals<-Journals[,c("subs","price")]
journals$citeprice<-Journals$price/Journals$citations
journals$lsubs<-log(journals$subs)
journals$lciteprice<-log(journals$citeprice)

plot(lsubs ~ lciteprice, data =journals)
jour_lm<-lm(lsubs ~ citeprice, data =journals)
abline(jour_lm)
linearHypothesis(jour_lm,"citeprice=-0.5")
```

```{r}
coef (jour_lm) 

confint(jour_lm, level = 0.95)
```

```
```{r}
predict(jour_lm, newdata = data.frame(lciteprice= c(2.11,3)),interval = "confidence")
x<-predict( jour_lm, newdata=data.frame(lciteprice = C(2.11,3)), interval ="prediction")
```
```{r}
mydatak- seq( from=-4, to = 2, by= 0.25)
jour_pred <- predict(jour_lm, interval = "prediction", newdata = data.frame(lciteprice = mydata))

plot(lsub~lciteprice,data=journals)
lines(jour_pred[, 1]~ mydata,col = 1)
lines(jour_pred[, 2]~mydata, col=1, lty=2)
lines(jour_pred[, 3]~mydata, col=1, lty=2)
```

